Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-19 arxiv/proof_gaussian_case.tex
appendix

\paragraph{Notations.}
We introduce several useful notations for the proof of Theorem \ref{thm_main_RMT}.
We say that an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
The following notion of stochastic domination, which was first introduced in \cite{Average_fluc}, is commonly used in the study of random matrices.

@@

\begin{fact}[Lemma 3.2 in \cite{isotropic}]\label{lem_stodomin}
Let $\xi$ and $\zeta$ be two families of nonnegative random variables depending on some parameters $u\in \cal U$ or $v\in \cal V$.
\begin{itemize}
\item[(i)] Suppose that $\xi (u,v)\prec \zeta(u,v)$ uniformly in $u\in \cal U$ and $v\in \cal V$. If $|\cal V|\le n^C$ for some constant $C>0$, then $\sum_{v\in \cal V} \xi(u,v) \prec \sum_{v\in \cal V} \zeta(u,v)$ uniformly in $u$.

>>>>

\paragraph{Notations.}
We introduce several useful notations for the proof of Theorem \ref{thm_main_RMT}.
We say that an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
The following notion of stochastic domination, which was first introduced in \citet{Average_fluc}, is commonly used in the study of random matrices.

@@

\begin{fact}[Lemma 3.2 in \citet{isotropic}]\label{lem_stodomin}
Let $\xi$ and $\zeta$ be two families of nonnegative random variables depending on some parameters $u\in \cal U$ or $v\in \cal V$.
\begin{itemize}
\item[(i)] Suppose that $\xi (u,v)\prec \zeta(u,v)$ uniformly in $u\in \cal U$ and $v\in \cal V$. If $|\cal V|\le n^C$ for some constant $C>0$, then $\sum_{v\in \cal V} \xi(u,v) \prec \sum_{v\in \cal V} \zeta(u,v)$ uniformly in $u$.
